Approximation as Differentiation: Notes

### 2025-05-25 main/higher-order.tex
Give the construction of the internal hom in Fam(C).

$\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed. Neither is therefore suitable for
interpreting higher-order programs. However the following is a special case of a construction due to
\citet{nunes2023}:

>>>>

$\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed, and therefore suitable for interpreting
higher-order programs. However the following is a special case of a construction due to \citet{nunes2023}:
